Manuscript_Github_Pchabaudi_calculateTPM

### 2022-07-21 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_calculateTPM.Rmd
Read in the correct data

#Colour blind friendly palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
show_col(cbPalette)

@@

```{r calc_tpm}

chab_count_table <- read.csv('Manuscript_Suppinfo_chabaudi_24h_counts.csv',
                             row.names = 1)

twentyfour_ct_comb <- tpm(count_data = chab_count_table, 
                          lengths = chabaudi_transcript_lengths)
```

>>>>

#Colour blind friendly palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#show_col(cbPalette)

@@

```{r calc_tpm}
#Read in the count data and remove one sample which is unknown and had no description.
chab_count_table <- read.csv('data/tl19-07_twentyfour_counts_samples.csv') %>% 
  select(-rMT_Unknown)
#Calculate the TPM
twentyfour_ct_comb <- tpm(count_data = chab_count_table, 
                          lengths = chabaudi_transcript_lengths)
```
